Dashboards for stock assessments: Getting started

### 2019-11-06 analysis/dashboards/getting_started.Rmd
Minor tweaks to getting started dashboard following workshop

````
```{r setup, include=FALSE} `r ''`
library(plotly)
library(crosstalk)
lw <- read.csv("length-weight_data.csv")
shared_lw <- SharedData$new(lw, ~record)
```
````

@@

```{r}
lw <- read.csv("length-weight_data.csv")
shared_lw <- SharedData$new(lw, ~record)
```

@@

>>>>

````
```{r setup, include=FALSE} `r ''`
library(plotly)
library(crosstalk)
lw <- read.csv("length-weight_data.csv")
shared_lw <- SharedData$new(lw)
```
````

@@

```{r}
lw <- read.csv("length-weight_data.csv")
shared_lw <- SharedData$new(lw)
```

@@

Also note that multiple pages can be generated using markdown's level 1 header:

Page 1
====================================

Page 2
====================================
